Crop adaptation with gene flow from wild relatives

### 2015-10-19 Li_outline.tex
Li made modifications

A recent study \cite{Wang2015manuscript} revealed that gene flow exist from \emph{mexicana} not only to Mexican highland maize, but also to Guatamalan highland maize, as well as to some individuals in Southwestern US Highland, suggesting different extent contributions \emph{mexicana} made to multiple maize highland landrace populations depending on the distance away from the distribution of \emph{mexicana}. 
The Andean maize, the population totally isolated from the occurrence of any teosinte species, underwent the severest historical bottleneck, as a population in the front wave of the serial founder effects. 
The stronger genetic drift introduced by the smaller historical population size improved the homozygosity but reduced the heterozygosity of the population, and it also extended the length of homozygosity.
The high frequency of deleterious alleles caused by stronger genetic drift in the Andes population, together with the reduced efficiency of selection against deleterious sites, contributes to the observed higher mutation load in the well-isolated maize population. 
Even though it is clear that the absence of introgression from wild relatives provided less genetic resource for the highland adaptation and thus made the highland adaptation unique in the Andes, it is yet unknown that out of reach of wild relatives is a reason for reduced fitness in the Andes population.
And the question whether convergent evolution occurs between populations with and without introgression from wild relatives is a key topic for future studies in maize.

>>>>

However, has the introgression from \emph{mexicana} spread to multiple highland populations? 
How does the adaptation differ among populations with and without introgression from \emph{mexicana}?
A recent study \cite{Wang2015manuscript} first utilized the ABBA-BABA statistics to evaluate the existence or absence of introgression from  \emph{mexicana} to multiple highland populations, and then $\hat{f_{d}}$ statistic proposed by Martin et al. (2015) \citep{martin2015} were calculated to locate the introgressed loci. 
Figure \ref{fig:fd} showed the loess regression of $\hat{f_{d}}$ in $10kb$ non\-overlapping windows across two chromosomes (chr4 and chr5) in multiple comparisons. 
On chromosome 4 (Figure \ref{fig:fd}) , Mexican highland (MexHigh) and Guatamalan highland (GuaHigh) exhibited strong evidence of introgression from \emph{mexicana}, and the peaks of distribution corresponded to the region identified in Hufford et al. (2013) \citep{hufford2013}. 
The signal of introgression is absent for the other three populations.
On chromosome 5, the signals of introgression (the peak region of the distribution) are present in MexHigh, GuaHigh and Southwestern US Highland (SW\_US), but not the other two.
More details on the other chromosomes could be referred to \cite{Wang2015manuscript}.
Overall, both analyses revealed that gene flow exist from \emph{mexicana} not only to MexHigh maize, but also to GuaHigh maize, as well as to some individuals in SW\_US, but not to the Andes and South American lowland (SA\_Low) populations, suggesting different extent contributions \emph{mexicana} made to multiple maize highland landrace populations. 
The Andean maize, the population totally isolated from the occurrence of any teosinte species, underwent the severest historical bottleneck, as a population in the front wave of the serial founder effects. 
%The stronger genetic drift introduced by the smaller historical population size improved the homozygosity but reduced the heterozygosity of the population, and it also extended the length of homozygosity.
The high frequency of deleterious alleles caused by stronger genetic drift in the Andes population, together with the reduced efficiency of selection against deleterious sites, contributes to the observed higher mutation load in the well-isolated maize population. 
Even though it is clear that the absence of introgression from wild relatives provided less genetic resource for the highland adaptation and thus made the highland adaptation unique in the Andes, it is yet unknown that out of reach of wild relatives is a reason for reduced fitness in the Andes population.
And the question whether convergent evolution occurs between populations with and without introgression from wild relatives is a key topic for future studies in maize.

\begin{figure*}[b]
\centering
\includegraphics[width=.45\textwidth]{FigsAndTables/fdTrackChr4AllPop}
\hspace{0.05\textwidth} 
\includegraphics[width=.45\textwidth]{FigsAndTables/fdTrackChr5AllPop}
\caption{Loess regression of $\hat{f_{d}}$ in $10kb$ non\-overlapping windows across the genome in   five independent comparisons: MexLow\-MexHigh\-mexicana\-outgroup, MexLow\-GuaHigh\-mexicana\-outgroup, MexLow\-SW\_US\-mexicana\-outgroup, MexLow\-Andes\-mexicana\-outgroup, MexLow\-SA_Low\-mexicana\-outgroup. A: Chromosome 4; B: Chromosome 5. \label{fig:fd}}
\end{figure*}
